---
title: "Untitled"
author: "SZ"
date: '2022-11-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(raster)       #Main raster library with nearly all functions used in this analysis
library(rgdal)        #Spatial library - most functions used from rgdal are for vectors (shapefiles)
library(dplyr)        #NOT spatial - this is a data wrangling library
library(ggplot2)
library(here)
library(tidyverse)
library(ncdf4)
library(raster)
library(RColorBrewer)
library(sf)
library(ncdf4)
library("viridis") 
#library(cmocean)#color map from 

library(dplyr)
library(ggplot2)
library(tidyr)
library(mlr)
library(clue)
library(clusterSim)
library(GGally)
library(psych)
library(DataExplorer)
#library(clValid)
library(sf)
library(mapview)
#source(here::here("R","setup.R"))
#source(here::here("R","directories_dell.R"))
source(here::here("R","directories_pcOffice_TAMARA.R"))
library(colorRamps)
col <- colorRamps::matlab.like2
trix_all<-file.path ("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/")
list.files(trix_all)
trix_all_files=list.files(trix_all,pattern="^TRIX.*nc", full.names=TRUE)

year <- c(2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)#Once you have a stack
trix_2017 <- nc_open("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc")
```



```{r 02_00 2017} 
#M_DO_0_0, M_CHL_0_0, M_DIN_0_0, M_TP_0_0, TRIX_0_0, M_DO_0_25, M_CHL_0_25, M_DIN_0_25, M_TP_0_25, TRIX_0_25, M_DO_0_150, M_CHL_0_150, M_DIN_0_150, M_TP_0_150, TRIX_0_150

o2_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc"), varname="M_DO_0_0")
chl_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc"), varname="M_CHL_0_0")
din_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc"), varname="M_DIN_0_0")
tp_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc"), varname="M_TP_0_0")
```


```{r 02_00 2017} 
#sal_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/.nc"), varname="xxx")
#temp_00_17<-stack(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atla/.nc"), varname="xxx")


date <- seq(as.Date("2017-01-01"),as.Date("2017-12-01"), "months")
#names(o2_00_17) <- date

#pr <- extract(o2_00_17)
#mean of all years
o2_00_17_mean <- calc(o2_00_17, mean, na.rm=TRUE)
chl_00_17_mean <- calc(chl_00_17, mean, na.rm=TRUE)
din_00_17_mean <- calc(din_00_17, mean, na.rm=TRUE)
tp_00_17_mean <- calc(tp_00_17, mean, na.rm=TRUE)
plot(o2_00_17_mean)
o2_00_17_mean_df <- rasterToPoints(o2_00_17_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(o2=layer)
chl_00_17_mean_df <- rasterToPoints(chl_00_17_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(chl=layer)
din_00_17_mean_df <- rasterToPoints(din_00_17_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(din=layer)
tp_00_17_mean_df <- rasterToPoints(tp_00_17_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(tp=layer)
#cad_17_00 <cbind(coordinates(o2_00_17_mean), v=values(o2_00_17_mean))
##https://stackoverflow.com/questions/45064450/converting-a-raster-to-a-csv-in-r
cadeau_00_17<- left_join(o2_00_17_mean_df,chl_00_17_mean_df,by=c("x","y")) %>% left_join(din_00_17_mean_df, by=c("x","y")) %>% left_join(tp_00_17_mean_df, by=c("x","y"))
cadeau_00_17

myvars <- c("o2","chl", "din", "tp")
cadeau_00_17_var <-cadeau_00_17[myvars]
cadeau_00_17_var<-as.data.frame(scale(cadeau_00_17_var))#TO CREATE STANDARDISED DATA

```

```{r cluster analysis}
#run simple cluster analysis
result1 <- kmeans(cadeau_00_17_var, centers=3, nstart=100)

size <- as.data.frame(result1$size)
```


##Elbow method
Recall that, the basic idea behind partitioning methods, such as k-means clustering, is to define clusters such that the total intra-cluster variation [or total within-cluster sum of square (WSS)] is minimized. The total WSS measures the compactness of the clustering and we want it to be as small as possible.

The Elbow method looks at the total WSS as a function of the number of clusters: One should choose a number of clusters so that adding another cluster doesn’t improve much better the total WSS.

The optimal number of clusters can be defined as follow:

Compute clustering algorithm (e.g., k-means clustering) for different values of k. For instance, by varying k from 1 to 10 clusters.
For each k, calculate the total within-cluster sum of square (wss).
Plot the curve of wss according to the number of clusters k.
The location of a bend (knee) in the plot is generally considered as an indicator of the appropriate number of clusters.
```{r cluster analysis}
# Find the optimal number of clusters with the elbow rule
K <- 16
dev_entro <- c()#empty vectors to keep the results
for(i in 2:K)
{
  k_means <- kmeans(cadeau_00_17_var, centers=i, nstart=100)
  dev_entro <- c(dev_entro, k_means$tot.withinss)
}


plot(2:K, dev_entro,
     type="b", pch = 21, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     main="Elbow rule")
axis(side=1, at=1:10)
```

```{r}
# Collect results for plotting
group_5 <- kmeans(cadeau_00_17_var, centers=5, nstart=100)
result_5 <- cbind(group_5$cluster,cadeau_00_17_var)
# Interpreting result
result_5$group <- as.factor(group_5$cluster) 
result_5$'group_5$cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51

library(DataExplorer)
plot_boxplot(result_5, by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_5, group_5$cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_5b <- cbind(group_5$cluster,cadeau_00_17)
result_5b$group <- as.factor(group_5$cluster) 
mapview(result_5b, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=10)

```

```{r}
# Collect results for plotting
group_8 <- kmeans(cadeau_00_17_var, centers=8, nstart=100)
result_8 <- cbind(group_8$cluster,cadeau_00_17_var)
# Interpreting result
result_8$group <- as.factor(group_8$cluster) 
result_8$'group_5$cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51

library(DataExplorer)
plot_boxplot(result_8, by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_8, group_8$cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_8b <- cbind(group_8$cluster,cadeau_00_17)
result_8b$group <- as.factor(group_8$cluster) 
mapview(result_8b, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=10)

```


```{r all year}

trix_all<-file.path ("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/")
list.files(trix_all)
trix_all_files=list.files(trix_all,pattern="^TRIX.*nc", full.names=TRUE)


na_shp <- readOGR("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/boundaries_domains/griglia+maschera_adriatico/adriatic_sea_msfd_4326.shp")



o2_0_0<-stack(trix_all_files, varname="M_DO_0_0")
CRS4326 <-CRS("+init=epsg:4326")
o2_0_0rpj <- projectRaster(o2_0_0, crs = CRS4326,over=T,progress='text')
   #o2_0_0mask<- mask(o2_0_0,na_shp, progress='text')
   #o2_0_0crop<- crop(o2_0_0mask,na_shp, progress='text')
            o2_0_0mask<- mask(o2_0_0rpj,na_shp, progress='text')
            o2_0_0crop<- crop(o2_0_0mask,na_shp, progress='text')

chl_0_0<-stack(trix_all_files, varname="M_CHL_0_0")
projection(chl_0_0) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"  
chl_0_0 <- projectRaster(chl_0_0, crs = CRS4326,over=T,progress='text')
  chl_0_0mask<- mask(chl_0_0,na_shp, progress='text')
  chl_0_0crop<- crop(chl_0_0mask,na_shp, progress='text')
 
din_0_0<-stack(trix_all_files, varname="M_DIN_0_0")
din_0_0 <- projectRaster(din_0_0, crs = CRS4326,over=T,progress='text')
   din_0_0mask<- mask(din_0_0,na_shp, progress='text')
   din_0_0crop<- crop(din_0_0mask,na_shp, progress='text')

tp_0_0<-stack(trix_all_files, varname="M_TP_0_0")
tp_0_0 <- projectRaster(tp_0_0, crs = CRS4326,over=T,progress='text')
 tp_0_0mask<- mask(tp_0_0,na_shp, progress='text')
 tp_0_0crop<- crop(tp_0_0mask,na_shp, progress='text')
#mean of all years
o2_00_mean <- calc(o2_0_0crop, mean, na.rm=TRUE)
chl_00_mean <- calc(chl_0_0crop, mean, na.rm=TRUE)
din_00_mean <- calc(din_0_0crop, mean, na.rm=TRUE)
tp_00_mean <- calc(tp_0_0crop, mean, na.rm=TRUE)


o2_00_mean_df <- rasterToPoints(o2_00_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(o2=layer) %>% mutate_at(1:2, round, 4)
chl_00_mean_df <- rasterToPoints(chl_00_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(chl=layer) %>% mutate_at(1:2, round, 4)
din_00_mean_df <- rasterToPoints(din_00_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(din=layer) %>% mutate_at(1:2, round, 4)
tp_00_mean_df <- rasterToPoints(tp_00_mean, na.rm=TRUE) %>% as.data.frame() %>% rename(tp=layer) %>% mutate_at(1:2, round, 4)
#write.csv(tp_00_mean_df, file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/tp_00_mean_df.csv"))


cadeau_00<- left_join(o2_00_mean_df,chl_00_mean_df,by=c("x","y")) %>% left_join(din_00_mean_df, by=c("x","y")) %>% left_join(tp_00_mean_df, by=c("x","y"))
cadeau_00

myvars <- c("o2","chl", "din", "tp")
cadeau_00_var <-cadeau_00[myvars]
cadeau_00_var<-as.data.frame(scale(cadeau_00_var))#TO CREATE STANDARDISED DATA

```

```{r dataset with t and s}
# estraiamo S e T superficiali da file che ho scaricato da flusxus. la struttura di questi file è differente da quelli denominati TRIX poichè lo script è di Maroc. Serve fare un check per verificare che vadano bene. 
#SOno comunque medie mensili dal 2006 al 2017.

#nei file sss sst c'è solo il layer superficiale che è quello che andrò ad esaminare ora
CRS4326 <-CRS("+init=epsg:4326")

trix_all<-file.path ("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/")
#per farlo funzionare fai prima correre l'altro codice
sss_all_files=list.files(trix_all,pattern="^SSS.*nc", full.names=TRUE)

sss_0_0<-stack(sss_all_files, varname="S")

extent(sss_0_0)=extent(o2_0_0)
res(sss_0_0)=res(o2_0_0)
projection(sss_0_0) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"  

sss_0_0_rpj <- projectRaster(sss_0_0, crs = CRS4326,over=T,progress='text')

ss_0_0mask<- mask(sss_0_0_rpj,na_shp, progress='text')
ss_0_0crop<- crop(ss_0_0mask,na_shp, progress='text')
ss_00_mean <- calc(ss_0_0crop, mean)
#writeRaster(ss_00_mean ,filename = file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/ss_00_mean.tif"), format="GTiff", overwrite=TRUE)

ss_00_mean_df <- rasterToPoints(ss_00_mean) %>% as.data.frame() %>% rename(ss=layer)%>% mutate_at(1:2, round, 4)
write.csv(ss_00_mean_df, file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/ss_00_mean_df_base.csv"))


cadeau_00_st<- left_join(cadeau_00,ss_00_mean_df,by=c("x","y")) 
cadeau_00_st


sst_all_files=list.files(trix_all,pattern="^SST.*nc", full.names=TRUE)
sst_0_0<-stack(sst_all_files, varname="T")

extent(sst_0_0)=extent(o2_0_0)
res(sst_0_0)=res(o2_0_0)
projection(sst_0_0) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"  
sst_0_0_rpj <- projectRaster(sst_0_0, crs = CRS4326,over=T,progress='text')

st_0_0mask<- mask(sst_0_0_rpj,na_shp, progress='text')
st_0_0crop<- crop(st_0_0mask,na_shp, progress='text')
st_00_mean <- calc(st_0_0crop, mean)
#writeRaster(ss_00_mean ,filename = file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/ss_00_mean.tif"), format="GTiff", overwrite=TRUE)

st_00_mean_df <- rasterToPoints(st_00_mean) %>% as.data.frame() %>% rename(sst=layer)%>% mutate_at(1:2, round, 4)
cadeau_00_st<- left_join(cadeau_00_st,st_00_mean_df,by=c("x","y"))


myvars <- c("o2","chl", "din", "tp","ss","sst")
cadeau_00_st_var <-cadeau_00_st[myvars]
cadeau_00_st_var<-as.data.frame(scale(cadeau_00_st_var))

write.csv(cadeau_00_st_var,file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st_var.csv"))
write.csv(cadeau_00_st,file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st.csv"))

cadeau_00_st_var <- read.csv(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st_var.csv")) 
cadeau_00_st <- read.csv(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st.csv")) 
```

```{r cluster analysis}
# Find the optimal number of clusters with the elbow rule
K <- 9
dev_entro <- c()#empty vectors to keep the results
for(i in 2:K)
{
  k_means <- kmeans(cadeau_00_st_var, centers=i, nstart=100)
  dev_entro <- c(dev_entro, k_means$tot.withinss)
}


plot(2:K, dev_entro,
     type="b", pch = 21, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     main="Elbow rule")
axis(side=1, at=1:10)
```

```{r 5}
# Collect results for plotting
group_5 <- kmeans(cadeau_00_st_var, centers=5, nstart=100)
result_5 <- cbind(group_5$cluster,cadeau_00_st_var)
# Interpreting result
result_5$group <- as.factor(group_5$cluster) 
result_5$'group_5$cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51

library(DataExplorer)
plot_boxplot(result_5, by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_5, group_5$cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_5b <- cbind(group_5$cluster,cadeau_00_st)
result_5b$group <- as.factor(group_5$cluster) 
mapview(result_5b, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=0.5)


result_cadeau_5trial_sf <- st_as_sf(result_5b, coords = c("x", "y"), crs = my.projection)
st_crs(result_cadeau_5trial_sf)
result_cadeau_5trial_sf<-st_rasterize(result_cadeau_5trial_sf  %>% dplyr::select(group, geometry))
stars::write_stars(result_cadeau_5trial_sf, file.path(dir_cluster, "result_cadeau_5trial_sf.tif"))


```

```{r 4}
# Collect results for plotting
group_4 <- kmeans(cadeau_00_st_var, centers=4, nstart=100)
result_4 <- cbind(group_4$cluster,cadeau_00_st_var)
# Interpreting result
result_4$group <- as.factor(group_4$cluster) 
result_4$'group_4$cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51

library(DataExplorer)
plot_boxplot(result_4, by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_4, group_4$cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_4b <- cbind(group_4$cluster,cadeau_00_st)
result_4b$group <- as.factor(group_4$cluster) 
mapview(result_4b, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=0.5)

```

```{r 16}
# Collect results for plotting
group_16 <- kmeans(cadeau_00_st_var, centers=16, nstart=100)
result_16 <- cbind(group_16$cluster,cadeau_00_st_var)
# Interpreting result
result_16$group <- as.factor(group_16$cluster) 
result_16$'group_16$cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51

library(DataExplorer)
plot_boxplot(result_16, by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_16, group_16$cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_16b <- cbind(group_16$cluster,cadeau_00_st)
result_16b$group <- as.factor(group_16$cluster) 
mapview(result_16b, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=0.5)

```


An R package for spatially-constrained clustering using either distance or covariance matrices. “Spatially-constrained” means that the data from which clusters are to be formed also map on to spatial reference points, and the constraint is that clusters must be spatially contiguous.
https://mpadge.github.io/spatialcluster/
```{r use spatial constraint}
#https://spatialanalysis.github.io/workshop-notes/spatial-autocorrelation.html
#----------------------
install.packages("rgeoda")
library(rgeoda)
library(sf)


library(caret)
library(doParallel)
library(arules)
cluster <- makeCluster(detectCores()-1)
registerDoParallel(cluster)

library(spdep)
library (spatialcluster)
library(sfExtras)
#remotes::install_github("spatialanalysis/sfExtras")

cadeau_00_st_var <- read.csv(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st_var.csv")) 
cadeau_00_st <- read.csv(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st.csv")) 

cadeau_00_st_var <- read.csv(file.path("~/github/sharemed_prep/trix_cadeau/cadeau_00_st_var.csv"))

#https://geodacenter.github.io/rgeoda/articles/rgeoda_tutorial.html
prj4string <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
my.projection <- st_crs(prj4string)





cadeau_00_st_lat_long_sf <- st_as_sf(cadeau_00_st, coords = c("x", "y"), crs = my.projection)
st_crs(cadeau_00_st_lat_long_sf)
queen_weights(cadeau_00_st_lat_long_sf , order=1,  precision_threshold = 0)
queen_w <- queen_weights(cadeau_00_st_lat_long_sf)
summary(queen_w)
nbrs <- get_neighbors(queen_w, idx = 3)
nbrs

clusters_cadeau <- redcap(4, queen_w,cadeau_00_st, "fullorder-completelinkage")
clusters_cadeau
#saveRDS(clusters_cadeau, file="clusters_cadeau.RData")

clusters_cadeau<- readRDS("clusters_cadeau.RData")

### try to do like with the others
result_cadeau_spat <- cbind(clusters_cadeau$Cluster,cadeau_00_st_var)
# Interpreting result
result_cadeau_spat$group <- as.factor(clusters_cadeau$Cluster) 
result_cadeau_spat$'cluster_cadeau$Cluster'<-NULL
# https://ggplot2.tidyverse.org/reference/geom_boxplot.html
# https://towardsdatascience.com/understanding-boxplots-5e2df7bcbd51


#install.packages("DataExplorer")
library(DataExplorer)
plot_boxplot(result_cadeau_spat , by="group", geom_boxplot_args=list("outlier.color"="blue"))
clusplot(result_cadeau_spat, cluster_cadeau$Cluster, main='2D representation of the Cluster solution',
         color=TRUE, shade=TRUE,
         labels=4, lines=0)
# Plot the lon-lat dist of our clustering
result_cadeau_spatb <- cbind(clusters_cadeau$Cluster,cadeau_00_st)
result_cadeau_spatb$group <- as.factor(clusters_cadeau$Cluster) 
write.csv(result_cadeau_spatb,"result_cadeau_spatb.csv")

# open libraries
library(tidyverse)
library(sf)
library(stars)

# rasterize based on geometry and a column named "value". Change the name of this column if necessary


      result_cadeau_4trial_spatb_sf <- st_as_sf(result_cadeau_spatb, coords = c("x", "y"), crs = my.projection)
st_crs(result_cadeau_4trial_spatb_sf)
result_cadeau_4trial_spatb_sf <-st_rasterize(result_cadeau_4trial_spatb_sf  %>% dplyr::select(group, geometry))
 write_stars(result_cadeau_4trial_spatb_sf, "result_cadeau_4trial_spatb_sf.tif")
mapview(result_cadeau_spatb, xcol = "x", ycol = "y", zcol="group",crs = 4269, grid = FALSE, cex=0.5)

```


```{r some try with other packages.not working}


st_write(cadeau_00_st_lat_long_sf,
         "G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st.shp", driver = "ESRI Shapefile")

cadeau_00_st_lat_long_shp <- readOGR(file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/cadeau_00_st.shp"))
cadeau_00_st_utm <- spTransform(cadeau_00_st_lat_long_sf , CRS("+proj=utm +zone=33
+ellps=WGS84 +datum=WGS84 +units=m +no_defs +towgs84=0,0,0"))

plot(cadeau_00_st_utm )
cadeau_00_st_utm_sf <- sf::st_as_sf(cadeau_00_st_utm)
cadeau_00_st_queen <- st_queen(cadeau_00_st_utm_sf )



options(repos = c(
                  mpadge = 'https://mpadge.r-universe.dev',
                  CRAN = 'https://cloud.r-project.org'))
install.packges ("spatialcluster")
remotes::install_git("https://codeberg.org/mpadge/spatialcluster")

library (spatialcluster)
scl <- scl_full (xy, dmat, ncl = 8)
plot (scl)
library(spdep)
install.packages('spDataLarge', repos='https://nowosad.github.io/drat/',
type='source')

library(geosphere)
mdist <- distm(pr_lat_long_sf )
```

