---
title: "plastic_data"
author: "SZ"
date: "9/3/2022"
output: html_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R","setup.R"))
#source(here::here("R","directories_dell.R"))
source(here::here("R","directories_pcOffice_TAMARA.R"))
dir_atlas <- file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas")

med_mask <- st_read(file.path(dir_atlas, "/boundaries_domains/World_Seas_IHO_v3/MED_regions_IHOv3.shp")) %>% 
  group_by(med)%>%
   summarise(geometry = sf::st_union(geometry)) %>%
   ungroup()
med_mask[1]
plot(med_mask)

```

capitaneria.d.porto <- read.csv("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/plastic/capitaneria d porto.csv", sep=";") %>% 
  rename(Latitude=X) %>% 
  rename(Longitude=Posizione) %>% 
  rename(Date=Data.ritrovamento) %>% 
  rename(weight=Peso.stimato.kg) %>% 
  select(Latitude,Longitude,weight,Date)
Reti.nella.Rete.Map <- read.csv("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/plastic/Reti nella Rete Map.csv", sep=";") %>% 
  mutate(Date=Data) %>% 
  rename(weight=X) %>% 
  select(Latitude,Longitude,weight,Date)


EMODNET_seafloor_litter_unrestricted_2021 <- read.csv("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/plastic/EMODNET_seafloor_litter_unrestricted_2021.csv", sep=",") %>% 
  mutate(Latitude=ShootLat) %>% 
  mutate(Longitude=ShootLong) %>% 
  mutate(weight=LT_Weigth) %>% 
  select(Latitude,Longitude,weight,Date)
EMODNET_seafloor_litter_unrestricted_2021 


ghostnetsl <-  rbind(capitaneria.d.porto ,Reti.nella.Rete.Map, EMODNET_seafloor_litter_unrestricted_2021) 
 gn <-  rbind(ghostnetsl,)

write.csv(ghostnetsl, "G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/plastic/ghostnets2.csv")


```{r}
#on qgis esporta
#ghostnets<- st_read(file.path(dir_atlas, "/plastic/ghostnets_all.shp")) %>% 
#  select(field_1)
ghostnets<- st_read(file.path(dir_atlas, "/plastic/emodnet_plastic_clean.shp"))%>% mutate(idnum ="1")
ghostnets$idnum<- as.numeric(ghostnets$idnum )

plot(ghostnets)
ghostnets <- ghostnets %>% sf::st_as_sf(coords = c("long","lat"), crs = 4326)
 
```
"G:\Il mio Drive\ASSEGNO DI RICERCA\SHAREMED_mio\wp4_atlas\plastic\EMODNET_seafloor_litter_unrestricted_2021.csv"
"G:\Il mio Drive\ASSEGNO DI RICERCA\SHAREMED_mio\wp4_atlas\plastic\capitaneria d porto.csv"
"G:\Il mio Drive\ASSEGNO DI RICERCA\SHAREMED_mio\wp4_atlas\plastic\Reti nella Rete Map.csv"

```{r}
grid_na <- st_read(file.path(dir_atlas, "/boundaries_domains/NA_grid1-36_0.028.shp")) %>% 
  select(id) %>%  st_set_crs(4326) %>% 
  mutate(num=1)
grid <- as(grid_na,  'Spatial')

#a <- grid %>% sf::st_join(ghostnets, left = TRUE)

a_na <- grid_na %>% sf::st_join(ghostnets, left = TRUE)
plot(grid); plot(ghostnets[1],add=TRUE)

a_na_sum <- a_na %>% 
 group_by(id) %>% 
  summarise(sum=sum(idnum, na.rm=T), geometry)
 
ggplot() + geom_sf(data = a_na_sum , aes(fill = sum))

grddf <- as.data.frame(grid_na)
ggplot()


#ghn <- as(ghostnets,  'Spatial')
#ghn <- crop(ghn, na_bound)
#ghn <- mask(ghn, na_bound)
#plot()
#ghn <- crop(ghn, grid)
#ghostnets <- SpatialPointsDataFrame(ghn)

#plot(ghn)
#med <- raster(file.path(dir_atlas, "/boundaries_domains/med2.tif"))
#



install.packages("spatialrisk")
library(spatialrisk)
gemeente_sf <- points_to_polygon( grid_na , ghostnets, sum(num, na.rm = TRUE))
```

```{r}
dt<-data.frame(lon=71.85,lat =31.12,val=3)
dt
plot(dt)
ras_dom<-raster(xmn=150, xmx=180, ymn=25, ymx=35,
                          crs="+proj=longlat +datum=WGS84 +no_defs ",
                          resolution=c(0.1,0.1), vals=NA)
ras_dom
coordinates(dt) <- ~ lon + lat # Convert data frame to spatial object
result <- rasterize(dt, ras_dom, "val", update = TRUE) # put point in raster
reslt # The resulting raster with the point added
plot(result)
```

