---
title: "TRIX_sharemed"
author: "SZ"
date: "28/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(raster)       #Main raster library with nearly all functions used in this analysis
library(rgdal)        #Spatial library - most functions used from rgdal are for vectors (shapefiles)
library(dplyr)        #NOT spatial - this is a data wrangling library
library(ggplot2)
library(here)
library(tidyverse)
library(ncdf4)
library(raster)
library(RColorBrewer)
library(sf)
library(ncdf4)
library("viridis") 
library(cmocean)#color map from 
source(here::here("R","setup.R"))
#source(here::here("R","directories_dell.R"))
source(here::here("R","directories_pcOffice_TAMARA.R"))
library(colorRamps)
col <- colorRamps::matlab.like2
trix_all<-file.path ("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/")
list.files(trix_all)
trix_all_files=list.files(trix_all,pattern="^TRIX.*nc", full.names=TRUE)


trix_2017 <- nc_open("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc")
trix_2017_00 <- stack("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc" ,varname="TRIX_0_0")
hist(trix_2017_00)
trix_2017_150 <- stack("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/TRIX/TRIX2017.nc" ,varname="TRIX_0_150")
```


```{r setup, include=FALSE}

hist(trix_2017_150)
plot(trix_2017_00, col=col(140))

trix_2017
```

## Trix index on the Cadeau dominio

 The TRIX index is based on four state variables (n ),
which are directly related to productivity: chlorophyll a
 (Chl, mg/m3 ), oxygen as the absolute percentage deviation
from oxygen saturation (DO, %), dissolved inorganic nitrogen
(DIN, mg/m3, and total phosphorous (TP, mg/m3.
In particular, DIND N-NO3 C N-NO2 C N-NH4  and DOD
|100- Ox | , where Ox  is the oxygen saturation. Each state
variable is scaled by the highest (Ui  ) and the lowest (Li  ) values
in the data time series, and TRIX is defined as


 $$TRIX= \frac {k}{n}\sum_{i=1}^n\frac{(logM_i-logL_i)}{(logU_i-logL_i)} $$
The TRIX index was developed b Vollenweider et al. (1992)


E. Fiori et al.: Trophic index (TRIX) values for the Adriatic Sea basin   

TRIX units |	Conditions  |Trophic state
-----------|--------------|--------------
0–4        | Oligotrophic |Elevated        	
4–5        |              |Good          	
5–6        |              |Mediocre     
6–10       |Eutrophic     |Bad     	

In addition to TRIX, an efficiency coefficient can also be
defined (Giovanardi and Vollenweider, 2004) as the logarithm
of the ratio between the two aggregated main components
of the TRIX. The efficiency coefficient can be considered a supplementary
index with which to evaluate the nutrient utilization of
the system. 

$$eff.coeff= log\biggl( \frac{Chl \times Do}{DIN \times TP}\biggl)$$

C'e' un file per anno
Ogni file contiene 5 variabili: TRIX, OXY_dev_da_sat_perc, DIN, TP, CHL in mg/m3
Ogni variabile contiene 12 frame (uno al mese)
Ci sono 3 calcoli delle medie verticali:
_0_0 solo strato superficiale
_0_25 media dei primi 25 m
_0_150 media dei primi 150 m
```{r signle year}
trix_2017 <- nc_open("C:/Users/Acer/Google Drive/ASSEGNO DI RICERCA/SHAREMED_mio/TRIX/TRIX2017.nc")

```

```{r TRIX 00_ 2006-2017}
year <- c(2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)#Once you have a stack 


trix_0_0<-stack(trix_all_files, varname="TRIX_0_0")

trix_0_150<-stack(trix_all_files, varname="TRIX_0_150")
#names(trix_0_0) <- paste0(rep(2006:2017, each=12),sep="_", 1:12)
#month(trix_0_0) <- paste0(rep(2006:2017, each=12),sep="_", 1:12)
#year <- format(as.Date(names(trix_0_0), format = "X%Y"), format = "%Y")
#month <- format(as.Date(names(trix_0_0), format = "X%Y_%d"), format = "%m")
#trix_0_0
#trix_0_0[[names]]

hist(trix_0_150)

# add time dimension and names
date <- seq(as.Date("2006-01-01"),as.Date("2017-12-01"), "months")

names(trix_0_0) <- date

#get the date from the names of the layers and extract the month
indices <- format(as.Date(names(trix_0_0), format = "X%Y.%m.%d"), format = "%m")
indices <- as.numeric(indices)
trix_0_0
```


```{r monthly mean}
MonthTRIX00<- stackApply(trix_0_0, indices, fun = mean)
names(MonthTRIX00) <- month.abb

cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
rasterVis::levelplot(MonthTRIX00,col.regions=colorRampPalette(rev(brewer.pal(11, 'RdBu'))))
col <- colorRamps::matlab.like2
rasterVis::levelplot(MonthTRIX00,col.regions=col(20), main="monthly mean")
```


```{r monthly sd}
sd_monthlyTrix00 <-  stackApply(trix_0_0, indices, fun = sd)
rasterVis::levelplot(sd_monthlyTrix00,col.regions=colorRampPalette((brewer.pal(16, 'Reds'))), main="monthly sd")
```


```{r TRY TRIX 00 12/2017}
plot(trix_0_0[[144]])
```
##calculate the climatological mean

```{r YEARLY AVERAGE TRIX}
year <- format(as.Date(names(trix_0_0), format = "X%Y"), format = "%Y")
yr_trix_00 = stackApply(trix_0_0, indices=year, fun=mean)

col <- colorRamps::matlab.like2
plot(yr_trix_00, col=col(40),  zlim = c(2, 7))
col <- colorRamps::matlab.like2
#rasterVis::levelplot(yr_trix_00,col.regions=col(20), main="monthly mean")
rasterVis::levelplot(yr_trix_00,col.regions=colorRampPalette((brewer.pal(9, 'YlOrBr'))), main="Annual mean")


```


```{r yearly sd}

sd_AnnualTrix00 <-  stackApply(trix_0_0, year, fun = sd)
rasterVis::levelplot(sd_AnnualTrix00,col.regions=colorRampPalette((brewer.pal(16, 'Reds'))), main="Year sd")
```


```{r}
plot(yr_trix_00[[12]], col=col(140), main="index_2017")

```

```{r}
# create histograms of each raster
hist(yr_trix_00, 
     xlim = c(0, 9))
```

```{r ANOMALY}
yr_trix_00 = stackApply(trix_0_0, indices=year, fun=mean)
summary(trix_0_0)
trix_00_2017 <- yr_trix_00[[12]]


anomalies_trix00<-overlay(yr_avg_18_chl_2,yr_avg_clim_chl_2 , fun=function(r1, r2){return(r1-r2)})
```
```{r 150}
year <- format(as.Date(names(trix_0_150), format = "X%Y"), format = "%Y")
yr_trix_150 = stackApply(trix_0_150, indices=year, fun=mean)

col <- colorRamps::matlab.like2
plot(yr_trix_00, col=col(40),  zlim = c(2, 7))
col <- colorRamps::matlab.like2
#rasterVis::levelplot(yr_trix_00,col.regions=col(20), main="monthly mean")
rasterVis::levelplot(yr_trix_00,col.regions=colorRampPalette((brewer.pal(9, 'YlOrBr'))), main="Annual mean")


```


```{r Intensity?}


trix_eutrof <- calc(trix_0_0, fun=function(x)
  {ifelse(x<4, 0, x)})
rasterVis::levelplot(trix_eutrof,col.regions=colorRampPalette((brewer.pal(9, 'YlOrBr'))), main="Annual mean")



#somma su climatologia con valori oligotrofici eliminati
trix_sum
trix_sum_yr = stackApply(trix_eutrof, fun=sum)#mi dà somma anno per anno
trix_sum <- calc(trix_eutrof, sum)
hist(trix_sum)
plot(trix_sum)
trix_sum                                  #0, 1034.393  (min, max)
     xlim = c(0, 9))
rasterVis::levelplot(trix_sum,col.regions=colorRampPalette((brewer.pal(9, 'YlOrBr'))), main="Annual mean")


trix_intensity <- calc(trix_sum, fun=function(x){ifelse(x=0,x, (x/max))}
                       
                        (max-min)/max)
```
```{r}
trix_0_150
summary(trix_0_150)
 #reclassify per avere presenza/assenza di eutrofia

trix_0_150_rec<-reclassify(trix_0_150, c(-Inf,3.99,0))     #tutti i valori da -inf a4(Fiore eurtrof!!) valgono zero
trix_0_150_rec<-reclassify(trix_0_150_rec, c(3.99,+Inf,1)) 
plot(trix_0_150_rec)
trix_0_150_cnt <- calc(trix_0_150_rec, fun=sum)        #Fiore dice che sotto è oligotr.
plot(trix_0_150_cnt)
```

#to rescale(rescale)
For reference, to simply scale between 0 and 1

mnv <- cellStats(s,'min')
mxv <- cellStats(s,'max')
x <- (s - mnv) / (mxv - mnv)
```{r}


mnv <- cellStats(trix_0_150_cnt,'min')
mxv <- cellStats(trix_0_150_cnt,'max')
x <- (trix_0_150_cnt - mnv) / (mxv - mnv)
plot(x)



trix_0_150_cnt_easy <- calc(trix_0_150, fun=function(x){sum(x>4)})   #funzionava uguale!
hist(log(trix_0_150_cnt))
plot(trix_0_150_cnt, col.regions=colorRampPalette((brewer.pal(16, 'Reds'))))

rasterVis::levelplot(x,col.regions=colorRampPalette((brewer.pal(16, 'Reds')))) 
writeRaster(x, file.path(dir_atlas,"TRIX/x.nc"))
x <- raster(file.path(dir_atlas,"TRIX/x.nc"))
rasterVis::levelplot(x,col.regions=colorRampPalette((brewer.pal(16, 'Oranges')))) 
```

