---
title: "fishing_density"
author: "SZ"
date: "21/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R","setup.R"))
#source(here::here("R","directories_dell.R"))
source(here::here("R","directories_pcOffice_TAMARA.R"))
dir_atlas <- file.path("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas")

med_mask <- st_read(file.path(dir_atlas, "boundaries_domains/World_Seas_IHO_v3/MED_regions_IHOv3.shp")) %>% 
  group_by(med)%>%
   summarise(geometry = sf::st_union(geometry)) %>%
   ungroup()
med_mask[1]
plot(med_mask)

fis_density <- raster(file.path(dir_atlas,"emodnet/vessel_density_emodnet/2020_st_01_avg.tif"))

projection(fis_density) <-"+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs "
proj_latlon <-  "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 

#rescale_fis_density <- projectRaster(fis_density, crs=proj_latlon,over=T,progress='text', filename=file.path(dir_atlas,"emodnet/vessel_density_emodnet/rescale_fis_density_2020_st_01_avg.tif"),overwrite=F)
rescale_fis_density <- raster(file.path(dir_atlas,"emodnet/vessel_density_emodnet/rescale_fis_density_2020_st_01_avg.tif"))

plot(rescale_fis_density)
```


```{r}
rgn_med <-  st_read(file.path(dir_B,"prep/spatial/tmp/Regions_atl_FAO.shp")) %>% 
  filter(F_CODE==37) %>% 
  summarise(geometry = sf::st_union(geometry)) %>%
  ungroup()
rs_fis_dens <- crop(rescale_fis_density,rgn_med)
plot(rs_fis_dens)
med <- raster(file.path(dir_atlas, "/boundaries_domains/med2.tif"))
projection(med ) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 
plot(med)
extent(rs_fis_dens) <- extent(med)
dns_med <-     mask(rescale_fis_density,rgn_med)
plot(dns_med)
plot(rgn_med, add=TRUE)
cntpnts <- c(0,0.5,2,5,10,20,100)
rasterVis::levelplot(dns_med, margin=list(axis=TRUE), at=cntpnts)

```
the data are highly skewed, I need to log transform them
```{r}
dns_med_log = calc(dns_med ,fun=function(x){log(x+1)},progress='text')
plot(dns_med_log)
maxValue(dns_med_log)
```


```{r}
hist(dns_med)
r.min = cellStats(dns_med_log , "min")
r.max = cellStats(dns_med_log , "max")
maxValue(dns_med)
dim(r.max)
```


```{r}
r.scale <- ((dns_med_log  - r.min) / (r.max - r.min) )
hist(r.scale)
cutpnts <- c(0,0.001,0.01,0.05,0.08,1)
rasterVis::levelplot(r.scale, margin=list(axis=TRUE), col.regions = colorRampPalette((brewer.pal(9, 'Oranges'))))
plot(r.scale)

```


```{r}
na_bound <- readOGR(file.path(dir_atlas,"boundaries_domains/NA_boundaries.shp"))
fish_density_na <- crop(r.scale, na_bound)
plot(r.scale)
rasterVis::levelplot(fish_density_na, margin=list(axis=TRUE), col.regions = colorRampPalette((brewer.pal(9, 'Oranges'))))
```
We ipothesised an impact of the ghost-nets large as 7 km (maximum lenght of the nets)

```{r}
grid_na <- st_read(file.path(dir_atlas, "/boundaries_domains/NA_grid1-36_0.028_equal.shp")) #%>% 
  select(id)

grid_na_csv <- read.csv("G:/Il mio Drive/ASSEGNO DI RICERCA/SHAREMED_mio/wp4_atlas/boundaries_domains/NA_grid1-36_0.028_equal.csv") %>% 
mutate(id=as.character(id))

#cells_raster <- rasterFromXYZ(NA_grid1.36_0.028)
#plot(cells_raster) 
grid_na <- as(grid_na,  'Spatial')
plot(grid_na)
class(grid_na)
grid_na_raster <-rasterize(grid_na,fish_density_na,field = grid_na$id,progress='text')
plot(grid_na_raster, border='blue')+
  plot(ghostnets, col="red" ,pch=3, add=TRUE)
summary(grid_na_raster)
extract(ghostnets,grid_na_raster,fun=sum)
```
```{r}
ghostnets
```

```{r}
r <- raster(extent(grid_na))
  r[] <- 1:ncell(r)
  r <- as(r, "SpatialPolygonsDataFrame")  

plot(r)
  plot(grid_na, add=TRUE) 
  
    r <- as(grid_na, "Spatial")  
    plot(r)
grid_na_raster <-fasterize::fasterize(r,med,field = "id")
plot(grid_na_raster)
    projectRaster(r, crs=proj_latlon,over=T,progress='text', filename=file.path(dir_atlas,"emodnet/vessel_density_emodnet/r_grid_na.tif"),overwrite=F)
 projection(r) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"    
    
#    int <- raster::intersect( r,ghostnets)
#    plot(int)
#    m <- rgeos::gIntersection( r,ghostnets, byid=TRUE)
#  row.names(m)
```

```{r}
plot(fish_density_na)+
plot(ghostnets, col="red" , add=TRUE)+
plot(r, add=TRUE)
class(ghostnets)
# Convert 'sp' object 'meuse' (i.e. SpatialPointsDataFrame) into 'sf' object
grid <- as(grid_na,  'Spatial')
projection(grid) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"  
ghn <- as(ghostnets,  'Spatial')
ghostnets <-  st_as_sf(ghostnets)
ghn<-  st_as_sf(ghn)
library(stars)
#grid s<-  st_as_stars(grid)
plot(grid)
proj4string(ghn)
proj4string(grid)

res2 <- over(ghn, grid)
res2
res2 <- unique(res2$id)
res3 <- over(grid,ghn)

sum(is.na(a$field_1)) 
6883-6826
plot(grid_na)+plot(ghn, add=TRUE)
```
```{r}
p
```

```{r}
fis_log <- calc(r.scale, fun=function(x)log(x+1))

summary(r.scale)

plot(fis_density)
fis_log <- calc(fis_density, fun=function(x)log(x+1))
plot(fis_log)
vals <- getValues(fis_log)
summary(vals)
hist(vals)
ref <- quantile(vals, 0.9999, na.rm=TRUE)
ref_add <- data.frame(year="2020", quantile_9999 = as.numeric(ref))
fisdensity_ref_pts <- rbind(fisdensity_ref_pts, ref_add)